ScPy: A SuperCollider Extension for Performing Numerical Computation via Embedded Python

### 2016-08-24 doc/paper.tex
typos and bibilography stuff

\usepackage{fancyhdr} \usepackage{hyperref} \usepackage{listings} \usepackage{minted}

@@

\title{ScPy: A SuperCollider Extension for Perforeing Numerical Computation via Embedded Python}

@@

Since \texttt{FFT} objects in SuperCollider operate on a single channel only, they must be placed
in \texttt{Array} objects to support multichannel audio. \texttt{Array}s can hold objects of any
type, so it is natural to convert them to Python \texttt{list} objects, which have similar
properties. However, this presents an interesting problem: multichannel \texttt{FFT} objects are
then converted to \texttt{lists} of \texttt{ndarray} objects in Python. These are a bit more
awkward to work with than basic \texttt{ndarray} objects, but can easily be converted using a call
to the \texttt{array} function in Python. This can be seen in practice on line 16 of
\autoref{lst:boilerplate}. Although it would be possible to do this conversion
automatically, it is left out for the purpose of not introducing a feature simply to work around an
incomplete implementation of \texttt{FFT} objects in SuperCollider. The current conversions will
continue to function as intended if \texttt{FFT} objects are given multichannel support in the
future.

@@

\section{Bibliography}

>>>>

\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{minted}
\usepackage[backend=bibtex]{biblatex}

\addbibresource{references.bib}

@@

\title{ScPy: A SuperCollider Extension for Performing Numerical Computation via Embedded Python}

@@

Since \texttt{FFT} objects in SuperCollider operate on a single channel only, they must be placed
in \texttt{Array} objects to support multichannel audio. \texttt{Array}s can hold objects of any
type, so it is natural to convert them to Python \texttt{list} objects, which have similar
properties. However, this presents an interesting problem: multichannel \texttt{FFT} objects are
then converted to \texttt{list}s of \texttt{ndarray} objects in Python. These are a bit more
awkward to work with than basic \texttt{ndarray} objects, but can easily be converted using a call
to the \texttt{array} function in Python. This can be seen in practice on line 16 of
\autoref{lst:boilerplate}. Although it would be possible to do this conversion
automatically, it is left out for the purpose of not introducing a feature simply to work around an
incomplete implementation of \texttt{FFT} objects in SuperCollider. The current conversions will
continue to function as intended if \texttt{FFT} objects are given multichannel support in the
future.

@@

\printbibliography
